The Near and Mid-infrared photometric properties of known redshift $z\geq5$ Quasars

### 2020-01-13 tex/MNRAS_submission/rv1/referees_reply.txt

	We have also made further, key improvements to our dataset and
	pipeline.

	We note that after the submission of the original manuscript
	it was brought to our attention (K. Perger; priv. comm) that
	we were missing 25 confirmed z>5 quasars.  As such, our
	database has increased by 25 objects for a total of 488 VHzQs.

	As such all six Tables have been updated accordingly, as have
	Figures 2 and 3.

	We also fully re-ran the WFCAM Science Archive (WSA) and VISTA
	Science Archive (VSA) from scratch with the set of updated
	objects. This uncovered a small matching bug for three objects
	in the WSA (no issues were found in the VSA rerun). One of
	these objects, however, is SDSS J2220-0101, which we thought
	had large photometric changes but now acknowledge this was due
	to an incorrect apertureID assignment, when the database was updated 
	with new data. The updated photometry for SDSS J2220-0101 has the  
	VSA J-band magnitude 20.32+/-0.07 mag AB and a WSA magnitude 20.30+/-0.15 mag AB.

	Consequently, we have changed the appropriate text (in the Abstract,
	Section 3.1.1 Comparing WFCAM and VISTA and Conclusions).

@@

		We have added approriated words in the text to address this good point.

p. 6 Table 3: Should mention that the number of significant digits listed here
for the YJHK W1--W4 mags is not always warranted, but needed to verify the small
VIRCAM-WFCAM offsets in Table 5, This table is a very useful check of your global
photometric zeropoints.

p. 7, very end of 3.1.1: Quote the (effective) VSA and SDSS quasar IR observing
epochs here, in case these clearly discrepant magnitudes are due to variability.

SDSS J0349+0034 was observed on MJD=54062.4 by WFCAM and MJD=55540.6 (average of 
3 epochs from 55537 to 55542) by VISTA. We have updated the text with these values.
We have also updated the values to AB magnitudes, as we found that we had inadvertently 
given the Vega magnitude values.

### 2020-01-13 tex/MNRAS_submission/rv1/VHzQ_MNRAS_rv1.tex
Fixed numbers for VegaToAB, added to referee reply

\maketitle
\begin{abstract}
We assemble a catalogue of 488 spectroscopically confirmed very high
($z\geq5.00$) redshift quasars and report their near- ($ZYJHK_{s}/K$)
and mid- (WISE W1234) infrared properties. 97\% of the VH$z$Q sample
is detected in one or more NIR ($ZYJHK/K_{s}$) band, with lack of
coverage rather than lack of depth being the reason for the
non-detections. 362 (78\%) of the very high redshift quasars are
detected at 3.4$\mu$m in the W1 band from the unWISE catalog and all
of the $z\geq7$ quasars are detected in both unWISE W1 and W2. Using
archival WFCAM/UKIRT and VIRCAM/VISTA data we check for photometric
variability that might be expected from super-Eddington accretion. We
find 32 of the quasars have sufficient NIR measurements and
signal-to-noise to look for variability. Weak variability was detected
in multiple bands of SDSS J0959+0227, and very marginally in the
$Y$-band of MMT J0215-0529. Only one quasar, SDSS J0349+0034, shows
significantdifferences between WFCAM and VISTA magnitudes in one band.
With supermassive black hole accretion likely to be redshift invariant
up to very high-redshift, further monitoring of these sources is
warranted.  All the data, analysis codes and plots used and generated
here can be found at:
\href{https://github.com/d80b2t/VHzQ}{\tt github.com/d80b2t/VHzQ}.
\end{abstract}

@@

  We have also checked for quasars with large differences in magnitude
  between the WSA and VSA. Objects were selected where the average flux
  was $>0.$ and $>5$ average flux error. In order to account for large
  errors in either the WFCAM or VISTA photometry, objects with
  $\delta$mag$ < 2 \times$ $\sigma_{\delta\rm mag}$ in either WSA or VSA
  were removed. This selects one quasar with large, $\delta$mag
  $>0.2$mag differences between the WSA and VSA. This is SDSSJ0349+0034
  which has a WSA $K$-band magnitude of 19.13$\pm$0.24 (observed at
  MJD=54062.4), while for the VSA $K_s$-band this is 18.36$\pm$0.10 mag
  (observed 3 times between MJD=55537 and 55542). The WFCAM and VISTA
  observations are $\sim4$ years apart.

>>>>

\maketitle
\begin{abstract}
We assemble a catalogue of 488 spectroscopically confirmed very high
($z\geq5.00$) redshift quasars and report their near- ($ZYJHK_{s}/K$)
and mid- (WISE W1234) infrared properties. 97\% of the VH$z$Q sample
is detected in one or more NIR ($ZYJHK/K_{s}$) band, with lack of
coverage rather than lack of depth being the reason for the
non-detections. 362 (78\%) of the very high redshift quasars are
detected at 3.4$\mu$m in the W1 band from the unWISE catalog and all
of the $z\geq7$ quasars are detected in both unWISE W1 and W2. Using
archival WFCAM/UKIRT and VIRCAM/VISTA data we check for photometric
variability that might be expected from super-Eddington accretion. We
find 32 of the quasars have sufficient NIR measurements and
signal-to-noise to look for variability. Weak variability was detected
in multiple bands of SDSS J0959+0227, and very marginally in the
$Y$-band of MMT J0215-0529. Only one quasar, SDSS J0349+0034, shows
significant differences between WFCAM and VISTA magnitudes in one band.
With supermassive black hole accretion likely to be redshift invariant
up to very high-redshift, further monitoring of these sources is
warranted.  All the data, analysis codes and plots used and generated
here can be found at:
\href{https://github.com/d80b2t/VHzQ}{\tt github.com/d80b2t/VHzQ}.
\end{abstract}

@@

  We have also checked for quasars with large differences in magnitude
  between the WSA and VSA. Objects were selected where the average flux
  was $>0.$ and $>5$ average flux error. In order to account for large
  errors in either the WFCAM or VISTA photometry, objects with
  $\delta$mag$ < 2 \times$ $\sigma_{\delta\rm mag}$ in either WSA or VSA
  were removed. This selects one quasar with large, $\delta$mag
  $>0.2$mag differences between the WSA and VSA. This is SDSSJ0349+0034
  which has a WSA $K$-band magnitude of 21.03$\pm$0.35 AB (observed at
  MJD=54062.4), while for the VSA $K_s$-band this is 20.21$\pm$0.14 mag AB
  (observed 3 times between MJD=55537 and 55542). The WFCAM and VISTA
  observations are $\sim4$ years apart.
